### 2018-06-21 draft.Rmd
add some small changes

## Noun classes in Zilo Andi: experimental data

@@

**Abstract**

@@

map.feature(coord$Language,
            features = coord$Language,
            latitude = coord$Lat,
            longitude = coord$Lon,
            label = coord$label,
            label.hide = FALSE,
            shape = TRUE,
            zoom.level = 11,
            tile = "Stamen.TonerBackground")
```

>>>>

## Noun classes in Zilo Andi: experimental data [^1]

@@

### Abstract

@@

map.feature(coord$Language,
            features = coord$Language,
            latitude = coord$Lat,
            longitude = coord$Lon,
            label = coord$label,
            label.hide = FALSE,
            label.fsize = 12,
            label.font = "Times New Roman",
            shape = TRUE,
            zoom.level = 11,
            tile = "Stamen.TonerBackground")
```
